---
title: 'Data simulator'
author: '<a href = "#section-summary"><span style = "color: #E9D6D6; font-weight: bold; border-bottom: 1.9px dotted grey;">`r reactive( try( if(nrow(dataset_summary()) > 1) paste(nrow(dataset_summary()), "cells"), silent = TRUE ) %>% gsub("\\Error.*", "", .))`</span></a>'
output:
  flexdashboard::flex_dashboard:
    theme: 'spacelab'
    orientation: columns
    vertical_layout: scroll
runtime: shiny
---

```{r setup, include = FALSE}

library(doBy)
library(knitr)
library(dplyr)
library(tidyr)
library(DT)
library(stringr)
library(purrr)
library(schoolmath)
library(ngram)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE)

```


<!-- Enable icons -->

<head>

<style type="text/css">

</style>

<!-- Load Bootstrap libraries for icons -->
<link rel='stylesheet' href='https://use.fontawesome.com/releases/v5.7.0/css/all.css' integrity='sha384-lZN37f5QGtY3VHgisS14W3ExzMWZxybE1SJSEsQp9S+oqd12jhcu+A56Ebc1zFSJ' crossorigin='anonymous'>

<!-- Javascript function to enable a hovering tooltip -->
<script>
$(document).ready(function(){
$('[data-toggle="tooltip1"]').tooltip();
});
</script>

////// Tooltip css styling
$("#message").css({
'font-size':'2px'
});

</head>



<i class="fas fa-info-circle"></i> Start
=======================================================================

Column
-----------------------------------------------------------------------

### <span style='font-size:18px; color:#4D4F54;'>Generating pseudo-random data sets to simulate participant-based experiments</span>

#### How to use

Independent variables are categorical and include between-group factors (distributing participants into different groups) and within-subject factors (administering a condition to all participants). Dependent variables are continuous.

#### Total sample size (*N*)

Based on the total *N* entered below, participants will be evenly distributed into any groups. Likewise, repeated measures are created for any within-subject conditions by expanding the number of rows in the long-format data set ([last tab](#dataset)). The Total *N* is interlocked with the factorial structure of the data set (if any has been created).

```{r}

tags$style(type = "text/css",
           "#Total_N.form-control.shiny-bound-input {padding-left:40px; padding-top:8px; padding-bottom:8px; font-size:150%; color:#1D510E; letter-spacing:4px;}")

numericInput('Total_N', '', 1, min = 1)

```

##### Between-group

The number of between-group levels ...

##### Within-subject

[in progress]

##### Dependent

[in progress]

###### Continuous

###### Categorical

#### <span style='font-weight:bold; font-size:15px;'>Ensuring reproducibility</span>

If you wish to ensure reproducibility, take the following steps. 

##### 1. Note the seed number or set a new one

A seed number is a code that allows the reproducibility of any data involving random generation. Please find your current seed number below, and feel free to note it down, or change it to any integer number within ± `r .Machine$integer.max`.

```{r}

tags$style(type = "text/css",
           "#seed.form-control.shiny-bound-input {padding-left:40px; padding-top:8px; padding-bottom:8px; font-size:150%; color:#206B90; letter-spacing:6px;}")

numericInput('seed', '', sample(1:99999, 1), min = 1, step = 1, max = .Machine$integer.max)

# The seed from input$seed should now be set before 
# any random sampling function, such as rnorm().

```

##### 2. Keep the information

Reproducing a simulation requires three pieces of data: the seed number, the parameter list and the final data set. Therefore, after creating the variables wanted, make sure to download the parameter list and the final data set in the [last tab](#dataset). Importantly, the names of both these files will contain the seed number displayed above these lines.

#### Referencing the app

Bernabeu, P., & Lynott, D. (2020). Experiment simulation app [Web application]. Retrieved from https://github.com/pablobernabeu/Experiment-Simulation/.

#### Code and contact

Please submit any questions or feedback by [posting an issue](https://github.com/pablobernabeu/Experiment-Simulation/blob/master/README.md) (recommended option) or by emailing p.bernabeu@lancaster.ac.uk.



Between-group
=======================================================================

Column
-----------------------------------------------------------------------

### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Between-group 1</span>

```{r}

textInput('name_BetweenGroup1', '', placeholder = 'Variable name')

textInput('BetweenGroup1_Group1', '', placeholder = 'Level 1')
textInput('BetweenGroup1_Group2', '', placeholder = 'Level 2')
textInput('BetweenGroup1_Group3', '', placeholder = 'Level 3')
textInput('BetweenGroup1_Group4', '', placeholder = 'Level 4')
textInput('BetweenGroup1_Group5', '', placeholder = 'Level 5')
textInput('BetweenGroup1_Group6', '', placeholder = 'Level 6')
textInput('BetweenGroup1_Group7', '', placeholder = 'Level 7')
textInput('BetweenGroup1_Group8', '', placeholder = 'Level 8')
textInput('BetweenGroup1_Group9', '', placeholder = 'Level 9')
textInput('BetweenGroup1_Group10', '', placeholder = 'Level 10')

```


Column
-----------------------------------------------------------------------

### <span style='font-weight:bold; font-size:15px; color:#001AB3;'>Between-group 2</span>

```{r}

textInput('name_BetweenGroup2', '', placeholder = 'Variable name')

textInput('BetweenGroup2_Group1', '', placeholder = 'Level 1')
textInput('BetweenGroup2_Group2', '', placeholder = 'Level 2')
textInput('BetweenGroup2_Group3', '', placeholder = 'Level 3')
textInput('BetweenGroup2_Group4', '', placeholder = 'Level 4')
textInput('BetweenGroup2_Group5', '', placeholder = 'Level 5')
textInput('BetweenGroup2_Group6', '', placeholder = 'Level 6')
textInput('BetweenGroup2_Group7', '', placeholder = 'Level 7')
textInput('BetweenGroup2_Group8', '', placeholder = 'Level 8')
textInput('BetweenGroup2_Group9', '', placeholder = 'Level 9')
textInput('BetweenGroup2_Group10', '', placeholder = 'Level 10')

```


Column
-----------------------------------------------------------------------

### <span style='font-weight:bold; font-size:15px; color:#B32600;'>Between-group 3</span>

```{r}

textInput('name_BetweenGroup3', '', placeholder = 'Variable name')

textInput('BetweenGroup3_Group1', '', placeholder = 'Level 1')
textInput('BetweenGroup3_Group2', '', placeholder = 'Level 2')
textInput('BetweenGroup3_Group3', '', placeholder = 'Level 3')
textInput('BetweenGroup3_Group4', '', placeholder = 'Level 4')
textInput('BetweenGroup3_Group5', '', placeholder = 'Level 5')
textInput('BetweenGroup3_Group6', '', placeholder = 'Level 6')
textInput('BetweenGroup3_Group7', '', placeholder = 'Level 7')
textInput('BetweenGroup3_Group8', '', placeholder = 'Level 8')
textInput('BetweenGroup3_Group9', '', placeholder = 'Level 9')
textInput('BetweenGroup3_Group10', '', placeholder = 'Level 10')

```



Within-subject
=======================================================================

Column
-----------------------------------------------------------------------

### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Within-subject 1</span>

```{r}

textInput('name_WithinSubject1', '', placeholder = 'Variable name')

textInput('WithinSubject1_Condition1', '', placeholder = 'Level 1')
textInput('WithinSubject1_Condition2', '', placeholder = 'Level 2')
textInput('WithinSubject1_Condition3', '', placeholder = 'Level 3')
textInput('WithinSubject1_Condition4', '', placeholder = 'Level 4')
textInput('WithinSubject1_Condition5', '', placeholder = 'Level 5')
textInput('WithinSubject1_Condition6', '', placeholder = 'Level 6')
textInput('WithinSubject1_Condition7', '', placeholder = 'Level 7')
textInput('WithinSubject1_Condition8', '', placeholder = 'Level 8')
textInput('WithinSubject1_Condition9', '', placeholder = 'Level 9')
textInput('WithinSubject1_Condition10', '', placeholder = 'Level 10')

```


Column
-----------------------------------------------------------------------

### <span style='font-weight:bold; font-size:15px; color:#001AB3;'>Within-subject 2</span>

```{r}

textInput('name_WithinSubject2', '', placeholder = 'Variable name')

textInput('WithinSubject2_Condition1', '', placeholder = 'Level 1')
textInput('WithinSubject2_Condition2', '', placeholder = 'Level 2')
textInput('WithinSubject2_Condition3', '', placeholder = 'Level 3')
textInput('WithinSubject2_Condition4', '', placeholder = 'Level 4')
textInput('WithinSubject2_Condition5', '', placeholder = 'Level 5')
textInput('WithinSubject2_Condition6', '', placeholder = 'Level 6')
textInput('WithinSubject2_Condition7', '', placeholder = 'Level 7')
textInput('WithinSubject2_Condition8', '', placeholder = 'Level 8')
textInput('WithinSubject2_Condition9', '', placeholder = 'Level 9')
textInput('WithinSubject2_Condition10', '', placeholder = 'Level 10')

```


Column
-----------------------------------------------------------------------

### <span style='font-weight:bold; font-size:15px; color:#B32600;'>Within-subject 3</span>

```{r}

textInput('name_WithinSubject3', '', placeholder = 'Variable name')

textInput('WithinSubject3_Condition1', '', placeholder = 'Level 1')
textInput('WithinSubject3_Condition2', '', placeholder = 'Level 2')
textInput('WithinSubject3_Condition3', '', placeholder = 'Level 3')
textInput('WithinSubject3_Condition4', '', placeholder = 'Level 4')
textInput('WithinSubject3_Condition5', '', placeholder = 'Level 5')
textInput('WithinSubject3_Condition6', '', placeholder = 'Level 6')
textInput('WithinSubject3_Condition7', '', placeholder = 'Level 7')
textInput('WithinSubject3_Condition8', '', placeholder = 'Level 8')
textInput('WithinSubject3_Condition9', '', placeholder = 'Level 9')
textInput('WithinSubject3_Condition10', '', placeholder = 'Level 10')

```



Dependent
=======================================================================

Column {data-width=2200px}
-----------------------------------------------------------------------

### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Setting parameters</span>

<div style='min-width: 400px; max-width: 600px;'>

Where any factors exist (whether between, within, or categorical dependent), each row in the table below will represent a unique combination of the levels of factors, which is known as a *cell* in the factorial design. When entering the means and standard deviations for a dependent variable, multiple values can be entered in the same field, each corresponding to a cell. These values should be separated by commas. For instance, for a 2x2 design (four cells), the means of a dependent variable may be entered as $234, 543, 657, 123$. The standard deviations may be entered as $10, 20, 25, 5$. Alternatively, fewer values (any fraction of the number of cells) could be entered (e.g., one or two values instead of four), but that would effectively cancel the overall difference between some factor levels.

Please note that the means and standard deviations entered here are used in a random simulation. Therefore, the final data will slightly differ, especially with smaller samples. Last, if you wish to ensure the reproducibility of the simulated data, please download the parameter list in the [last tab](#dataset), and the [final data set](#dataset), and keep the seed number (`r reactive(input$seed)`, also shown in the names of the downloaded files).

</div>

```{r}

dataset_summary = reactive({
  
  # Create grouping cluster
  summary_by_factors = dataset() %>%
    group_by_at(vars(which(names(.) %in% c('BetweenGroup1', 'BetweenGroup2', 'BetweenGroup3',
                                           'WithinSubject1', 'WithinSubject2', 'WithinSubject3',
                                           'Categorical_Dependent1', 'Categorical_Dependent2',
                                           'Categorical_Dependent3', 'Categorical_Dependent4'))))
  
  # Basic structure to be expanded below where necessary
  summary = summary_by_factors %>% tally()
  
  if(!isTruthy(input$name_Continuous_Dependent1) & !isTruthy(input$name_Continuous_Dependent2) &
     !isTruthy(input$name_Continuous_Dependent3) & !isTruthy(input$name_Continuous_Dependent4)) {
    summary
  }
  
  if(isTruthy(input$name_Continuous_Dependent1)) {
    summary = summary_by_factors %>%
      summarise(Dependent1_Mean = mean(Continuous_Dependent1) %>% round(digits = 3),
                Dependent1_SD = sd(Continuous_Dependent1) %>% round(digits = 3),
                n = n())
  }
  
  if(isTruthy(input$name_Continuous_Dependent2)) {
    summary = summary_by_factors %>%
      summarise(Dependent1_Mean = mean(Continuous_Dependent1) %>% round(digits = 3),
                Dependent1_SD = sd(Continuous_Dependent1) %>% round(digits = 3),
                Dependent2_Mean = mean(Continuous_Dependent2) %>% round(digits = 3),
                Dependent2_SD = sd(Continuous_Dependent2) %>% round(digits = 3),
                n = n())
  }
  
  if(isTruthy(input$name_Continuous_Dependent3)) {
    summary = summary_by_factors %>%
      summarise(Dependent1_Mean = mean(Continuous_Dependent1) %>% round(digits = 3),
                Dependent1_SD = sd(Continuous_Dependent1) %>% round(digits = 3),
                Dependent2_Mean = mean(Continuous_Dependent2) %>% round(digits = 3),
                Dependent2_SD = sd(Continuous_Dependent2) %>% round(digits = 3),
                Dependent3_Mean = mean(Continuous_Dependent3) %>% round(digits = 3),
                Dependent3_SD = sd(Continuous_Dependent3) %>% round(digits = 3),
                n = n())
  }
  
  if(isTruthy(input$name_Continuous_Dependent4)) {
    summary = summary_by_factors %>%
      summarise(Dependent1_Mean = mean(Continuous_Dependent1) %>% round(digits = 3),
                Dependent1_SD = sd(Continuous_Dependent1) %>% round(digits = 3),
                Dependent2_Mean = mean(Continuous_Dependent2) %>% round(digits = 3),
                Dependent2_SD = sd(Continuous_Dependent2) %>% round(digits = 3),
                Dependent3_Mean = mean(Continuous_Dependent3) %>% round(digits = 3),
                Dependent3_SD = sd(Continuous_Dependent3) %>% round(digits = 3),
                Dependent4_Mean = mean(Continuous_Dependent4) %>% round(digits = 3),
                Dependent4_SD = sd(Continuous_Dependent4) %>% round(digits = 3),
                n = n())
  }
  
  # Rename columns or remove if not included by user
  
  if(isTruthy(input$name_BetweenGroup1)) {
    names(summary)[names(summary)=="BetweenGroup1"] = input$name_BetweenGroup1
  }
  
  if(isTruthy(input$name_BetweenGroup2)) {
    names(summary)[names(summary)=="BetweenGroup2"] = input$name_BetweenGroup2
  }
  
  if(isTruthy(input$name_BetweenGroup3)) {
    names(summary)[names(summary)=="BetweenGroup3"] = input$name_BetweenGroup3
  }
  
  if(isTruthy(input$name_WithinSubject1)) {
    names(summary)[names(summary)=="WithinSubject1"] = input$name_WithinSubject1
  }
  
  if(isTruthy(input$name_WithinSubject2)) {
    names(summary)[names(summary)=="WithinSubject2"] = input$name_WithinSubject2
  }
  
  if(isTruthy(input$name_WithinSubject3)) {
    names(summary)[names(summary)=="WithinSubject3"] = input$name_WithinSubject3
  }
  
  if(isTruthy(input$name_Continuous_Dependent1)) {
    names(summary)[names(summary)=="Dependent1_Mean"] = paste0(input$name_Continuous_Dependent1, '_Mean')
    names(summary)[names(summary)=="Dependent1_SD"] = paste0(input$name_Continuous_Dependent1, '_SD')
  }
  
  if(isTruthy(input$name_Continuous_Dependent2)) {
    names(summary)[names(summary)=="Dependent2_Mean"] = paste0(input$name_Continuous_Dependent2, '_Mean')
    names(summary)[names(summary)=="Dependent2_SD"] = paste0(input$name_Continuous_Dependent2, '_SD')
  }
  
  if(isTruthy(input$name_Continuous_Dependent3)) {
    names(summary)[names(summary)=="Dependent3_Mean"] = paste0(input$name_Continuous_Dependent3, '_Mean')
    names(summary)[names(summary)=="Dependent3_SD"] = paste0(input$name_Continuous_Dependent3, '_SD')
  }
  
  if(isTruthy(input$name_Continuous_Dependent4)) {
    names(summary)[names(summary)=="Dependent4_Mean"] = paste0(input$name_Continuous_Dependent4, '_Mean')
    names(summary)[names(summary)=="Dependent4_SD"] = paste0(input$name_Continuous_Dependent4, '_SD')
  }
  
  if(isTruthy(input$name_Categorical_Dependent1)) {
    names(summary)[names(summary)=="Categorical_Dependent1"] = input$name_Categorical_Dependent1
  }
  
  if(isTruthy(input$name_Categorical_Dependent2)) {
    names(summary)[names(summary)=="Categorical_Dependent2"] = input$name_Categorical_Dependent2
  }
  
  if(isTruthy(input$name_Categorical_Dependent3)) {
    names(summary)[names(summary)=="Categorical_Dependent3"] = input$name_Categorical_Dependent3
  }
  
  if(isTruthy(input$name_Categorical_Dependent4)) {
    names(summary)[names(summary)=="Categorical_Dependent4"] = input$name_Categorical_Dependent4
  }
  
  # Because variables with original names remain in the data set (some bug), remove any such variables
  
  # summary = summary[, -grep('^BetweenGroup1|^BetweenGroup2|^BetweenGroup3|^WithinSubject1|^WithinSubject2|^WithinSubject3',
  #                            colnames(summary))]
  # 
  # summary = summary[, -grep('^Dependent1_Mean|^Dependent2_Mean|^Dependent3_Mean|^Dependent4_Mean',
  #                            colnames(summary))]
  # 
  # summary = summary[, -grep('^Dependent1_SD|^Dependent2_SD|^Dependent3_SD|^Dependent4_SD',
  #                            colnames(summary))]
  # 
  # summary = summary[, -grep('^Categorical_Dependent1|^Categorical_Dependent2|^Categorical_Dependent3|^Categorical_Dependent4',
  #                            colnames(summary))]
  
  # summary = summary %>%
  #   select_at(-vars(which(names(.) %in% c('BetweenGroup1', 'BetweenGroup2', 'BetweenGroup3',
  #                                         'WithinSubject1', 'WithinSubject2', 'WithinSubject3',
  #                                         'Dependent1_Mean', 'Dependent2_Mean',
  #                                         'Dependent3_Mean', 'Dependent4_Mean',
  #                                         'Dependent1_SD', 'Dependent2_SD',
  #                                         'Dependent3_SD', 'Dependent4_SD',
  #                                         'Categorical_Dependent1', 'Categorical_Dependent2',
  #                                         'Categorical_Dependent3', 'Categorical_Dependent4'))))
  
  # summary = summary %>% select(-one_of(starts_with('BetweenGroup1'), starts_with('BetweenGroup2'), starts_with('BetweenGroup3'),
  #                                      starts_with('WithinSubject1'), starts_with('WithinSubject2'), starts_with('WithinSubject3'),
  #                                      starts_with('Dependent1_Mean'), starts_with('Dependent2_Mean'),
  #                                      starts_with('Dependent3_Mean'), starts_with('Dependent4_Mean'),
  #                                      starts_with('Dependent1_SD'), starts_with('Dependent2_SD'),
  #                                      starts_with('Dependent3_SD'), starts_with('Dependent4_SD'),
  #                                      starts_with('Categorical_Dependent1'), starts_with('Categorical_Dependent2'),
  #                                      starts_with('Categorical_Dependent3'), starts_with('Categorical_Dependent4')))
  
  # Count observations per cell
  summary = 
    
    # Remove NA-only columns
    summary = summary[, !map_lgl(summary, ~ all(is.na(.)))]
  
  summary
  
})


renderDT({
  datatable(dataset_summary(), extensions = c('Buttons', 'FixedHeader'), class = 'compact cell-border',
            options = list(order = list(1, 'asc'), dom = 'Bifrt', scroller = TRUE, fixedHeader = TRUE,
                           buttons = list(list(extend = 'csv',
                                               filename = paste0('Summary of simulation using seed number ', input$seed, ' - retrieved ',
                                                                 str_replace_all(format(Sys.time(), '%d-%b-%Y_%X-%Z'), ':', '-') %>% 
                                                                   str_replace_all('\\ ', '-'), ' - ',
                                                                 'info on GitHub repository pablobernabeu data-simulation-app')),
                                          list(extend = 'excel',
                                               filename = paste0('Summary of simulation using seed number ', input$seed, ' - retrieved ',
                                                                 str_replace_all(format(Sys.time(), '%d-%b-%Y_%X-%Z'), ':', '-') %>% 
                                                                   str_replace_all('\\ ', '-'), ' - ',
                                                                 'info on GitHub repository pablobernabeu data-simulation-app'))),
                           pageLength = nrow(dataset_summary())),
            selection = 'none')
})

```


### Parameter list

```{r}

# Save parameter list

parameters = reactive({
  
  parameters = paste0('\nTotal sample size (N): ', input$Total_N, '\n')
  
  if(isTruthy(input$name_BetweenGroup1)) {
    parameters = paste0(parameters, '\n', 'Between-group factor 1', ': ', input$name_BetweenGroup1, '\n',
                        'Levels: ',
                        paste(input$BetweenGroup1_Group1, input$BetweenGroup1_Group2, input$BetweenGroup1_Group3,
                              input$BetweenGroup1_Group4, input$BetweenGroup1_Group5, input$BetweenGroup1_Group6,
                              input$BetweenGroup1_Group7, input$BetweenGroup1_Group8, input$BetweenGroup1_Group9,
                              input$BetweenGroup1_Group10, sep = ', ') %>%
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('^*\\, $', ''),
                        '\n')
  }
  
  if(isTruthy(input$name_BetweenGroup2)) {
    parameters = paste0(parameters, '\n', 'Between-group factor 2', ': ', input$name_BetweenGroup2, '\n',
                        'Levels: ',
                        paste(input$BetweenGroup2_Group1, input$BetweenGroup2_Group2, input$BetweenGroup2_Group3,
                              input$BetweenGroup2_Group4, input$BetweenGroup2_Group5, input$BetweenGroup2_Group6,
                              input$BetweenGroup2_Group7, input$BetweenGroup2_Group8, input$BetweenGroup2_Group9,
                              input$BetweenGroup2_Group10, sep = ', ') %>%
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('^*\\, $', ''),
                        '\n')
  }
  
  if(isTruthy(input$name_BetweenGroup3)) {
    parameters = paste0(parameters, '\n', 'Between-group factor 3', ': ', input$name_BetweenGroup3, '\n',
                        'Levels: ',
                        paste(input$BetweenGroup3_Group1, input$BetweenGroup3_Group2, input$BetweenGroup3_Group3,
                              input$BetweenGroup3_Group4, input$BetweenGroup3_Group5, input$BetweenGroup3_Group6,
                              input$BetweenGroup3_Group7, input$BetweenGroup3_Group8, input$BetweenGroup3_Group9,
                              input$BetweenGroup3_Group10, sep = ', ') %>%
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('^*\\, $', ''),
                        '\n')
  }
  
  if(isTruthy(input$name_WithinSubject1)) {
    parameters = paste0(parameters, '\n', 'Within-subject factor 1', ': ', input$name_WithinSubject1, '\n',
                        'Levels: ',
                        paste(input$WithinSubject1_Condition1, input$WithinSubject1_Condition2, input$WithinSubject1_Condition3,
                              input$WithinSubject1_Condition4, input$WithinSubject1_Condition5, input$WithinSubject1_Condition6,
                              input$WithinSubject1_Condition7, input$WithinSubject1_Condition8, input$WithinSubject1_Condition9,
                              input$WithinSubject1_Condition10, sep = ', ') %>%
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('^*\\, $', ''),
                        '\n')
  }
  
  if(isTruthy(input$name_WithinSubject2)) {
    parameters = paste0(parameters, '\n', 'Within-subject factor 2', ': ', input$name_WithinSubject2, '\n',
                        'Levels: ',
                        paste(input$WithinSubject2_Condition1, input$WithinSubject2_Condition2, input$WithinSubject2_Condition3,
                              input$WithinSubject2_Condition4, input$WithinSubject2_Condition5, input$WithinSubject2_Condition6,
                              input$WithinSubject2_Condition7, input$WithinSubject2_Condition8, input$WithinSubject2_Condition9,
                              input$WithinSubject2_Condition10, sep = ', ') %>%
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('^*\\, $', ''),
                        '\n')
  }
  
  if(isTruthy(input$name_WithinSubject3)) {
    parameters = paste0(parameters, '\n', 'Within-subject factor 3', ': ', input$name_WithinSubject3, '\n',
                        'Levels: ',
                        paste(input$WithinSubject3_Condition1, input$WithinSubject3_Condition2, input$WithinSubject3_Condition3,
                              input$WithinSubject3_Condition4, input$WithinSubject3_Condition5, input$WithinSubject3_Condition6,
                              input$WithinSubject3_Condition7, input$WithinSubject3_Condition8, input$WithinSubject3_Condition9,
                              input$WithinSubject3_Condition10, sep = ', ') %>%
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% str_replace_all('\\, \\,', ',') %>% 
                          str_replace_all('^*\\, $', ''),
                        '\n')
  }
  
  if(isTruthy(input$name_Continuous_Dependent1)) {
    parameters = paste0(parameters, '\n', 'Continuous dependent variable 1', ': ', input$name_Continuous_Dependent1,
                        '\nMean(s): ', input$mean1, '\nSD(s): ', input$sd1, '\n')
  }
  
  if(isTruthy(input$name_Continuous_Dependent2)) {
    parameters = paste0(parameters, '\n', 'Continuous dependent variable 2', ': ', input$name_Continuous_Dependent2,
                        '\nMean(s): ', input$mean2, '\nSD(s): ', input$sd2, '\n')
  }
  
  if(isTruthy(input$name_Continuous_Dependent3)) {
    parameters = paste0(parameters, '\n', 'Continuous dependent variable 3', ': ', input$name_Continuous_Dependent3,
                        '\nMean(s): ', input$mean3, '\nSD(s): ', input$sd3, '\n')
  }
  
  if(isTruthy(input$name_Continuous_Dependent4)) {
    parameters = paste0(parameters, '\n', 'Continuous dependent variable 4', ': ', input$name_Continuous_Dependent4,
                        '\nMean(s): ', input$mean4, '\nSD(s): ', input$sd4, '\n')
  }
  
  if(isTruthy(input$name_Categorical_Dependent1)) {
    parameters = paste0(parameters, '\n', 'Categorical dependent variable 1', ': ', input$name_Categorical_Dependent1,
                        '\nLevels: ', input$levels_categorical_dependent1, '\nProbability/ies: ', 
                        input$probability_categorical_dependent1, '\n')
  }
  
  if(isTruthy(input$name_Categorical_Dependent2)) {
    parameters = paste0(parameters, '\n', 'Categorical dependent variable 2', ': ', input$name_Categorical_Dependent2,
                        '\nLevels: ', input$levels_categorical_dependent2, '\nProbability/ies: ', 
                        input$probability_categorical_dependent2, '\n')
  }
  
  if(isTruthy(input$name_Categorical_Dependent3)) {
    parameters = paste0(parameters, '\n', 'Categorical dependent variable 3', ': ', input$name_Categorical_Dependent3,
                        '\nLevels: ', input$levels_categorical_dependent3, '\nProbability/ies: ', 
                        input$probability_categorical_dependent3, '\n')
  }
  
  if(isTruthy(input$name_Categorical_Dependent4)) {
    parameters = paste0(parameters, '\n', 'Categorical dependent variable 4', ': ', input$name_Categorical_Dependent4,
                        '\nLevels: ', input$levels_categorical_dependent4, '\nProbability/ies: ', 
                        input$probability_categorical_dependent4, '\n')
  }
  
  parameters
})


# Print list
reactive(cat(parameters()))

# Enable download -- link shown in last tab

# Create the actual downloadLink
output$parameters_download_link = renderUI({
  downloadLink('parameters_download', HTML('&nbsp; Download parameter list'), class = 'fa fa-download', style = 'border-bottom:none !important')
})

# Add download handling
output$parameters_download = downloadHandler(
  filename = function() {
    paste0('Parameter list (seed number ', input$seed, ') - retrieved ',
           str_replace_all(format(Sys.time(), '%d-%b-%Y_%X-%Z'), ':', '-') %>%
             str_replace_all('\\ ', '-'), ' - ',
           'info on GitHub repository pablobernabeu data-simulation-app.txt')
  },
  content = function(file) { cat(parameters(), file = file) }
)

```



Column
-----------------------------------------------------------------------

### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Continuous 1</span>

```{r}

textInput('name_Continuous_Dependent1', '', placeholder = 'Variable name')
textInput('mean1', '', placeholder = 'Mean(s)')
textInput('sd1', '', placeholder = 'Standard deviation(s)')

```


### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Continuous 2</span>

```{r}

textInput('name_Continuous_Dependent2', '', placeholder = 'Variable name')
textInput('mean2', '', placeholder = 'Mean(s)')
textInput('sd2', '', placeholder = 'Standard deviation(s)')

```


### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Continuous 3</span>

```{r}

textInput('name_Continuous_Dependent3', '', placeholder = 'Variable name')
textInput('mean3', '', placeholder = 'Mean(s)')
textInput('sd3', '', placeholder = 'Standard deviation(s)')

```


### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Continuous 4</span>

```{r}

textInput('name_Continuous_Dependent4', '', placeholder = 'Variable name')
textInput('mean4', '', placeholder = 'Mean(s)')
textInput('sd4', '', placeholder = 'Standard deviation(s)')

```



Column
-----------------------------------------------------------------------

### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Categorical 1</span>

```{r}

textInput('name_Categorical_Dependent1', '', placeholder = 'Variable name')
textInput('levels_categorical_dependent1', '', placeholder = 'Levels')
textInput('probability_categorical_dependent1',
          HTML('<span data-toggle="tooltip1" data-placement="right" title="Proportion of each level, overall or per cell (comma-separated), with values between 0 and 1. Values toward 0 increase proportion of first-entered levels; values toward 1 increase last-entered levels. Please check result, and if necessary, rearrange levels or increase sample size." style="border-bottom: 0.9px dotted grey;"><b> Probability </b><i class="fas fa-info-circle"></i></span>'),
          placeholder = 'Probability/ies')

reactive({
  
  if(isTruthy(input$probability_categorical_dependent1)) {
    
    Categorical_Dependent1 = rbinom(input$Total_N,
                                 # Below, count number of levels
                                 ngram::wordcount(input$levels_categorical_dependent1) - 1,  # One has to be subtracted for rbinom() to be be accurate
                                 eval(parse(text = paste0('c(', input$probability_categorical_dependent1, ')'))))
    
    # Place quotes around each factor level
    levels_categorical_dependent1 = sapply(strsplit(input$levels_categorical_dependent1, '[, ]+'), function(x) toString(dQuote(x)))
    
    # Wrap levels in c()
    levels_categorical_dependent1 = eval(parse(text = paste0('c(', levels_categorical_dependent1, ')')))
    
    Categorical_Dependent1 = as.factor(Categorical_Dependent1)
    levels(Categorical_Dependent1) = levels_categorical_dependent1
    
    cat('Overall proportion of each level\n~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\n')
    Categorical_Dependent1 %>% levels() %>%
      paste0(., ': ', table(Categorical_Dependent1) / sum(table(Categorical_Dependent1)) * 100, '%', collapse = '\n') %>%
      paste0(., '\n') %>% cat
    cat('\nTo see proportions in each cell,\nplease refer to summary table.')
    
  }
})

```


### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Categorical 2</span>

```{r}

textInput('name_Categorical_Dependent2', '', placeholder = 'Variable name')
textInput('levels_categorical_dependent2', '', placeholder = 'Levels')
textInput('probability_categorical_dependent2',
          HTML('<span data-toggle="tooltip1" data-placement="right" title="Proportion of each level, overall or per cell (comma-separated), with values between 0 and 1. Values toward 0 increase proportion of first-entered levels; values toward 1 increase last-entered levels. Please check result, and if necessary, rearrange levels or increase sample size." style="border-bottom: 0.9px dotted grey;"><b> Probability </b><i class="fas fa-info-circle"></i></span>'),
          placeholder = 'Probability/ies')

reactive({
  
  if(isTruthy(input$probability_categorical_dependent2)) {
    
    Categorical_Dependent2 = rbinom(input$Total_N,
                                 # Below, count number of levels
                                 ngram::wordcount(input$levels_categorical_dependent2) - 1,  # One has to be subtracted for rbinom() to be be accurate
                                 eval(parse(text = paste0('c(', input$probability_categorical_dependent2, ')'))))
    
    # Place quotes around each factor level
    levels_categorical_dependent2 = sapply(strsplit(input$levels_categorical_dependent2, '[, ]+'), function(x) toString(dQuote(x)))
    
    # Wrap levels in c()
    levels_categorical_dependent2 = eval(parse(text = paste0('c(', levels_categorical_dependent2, ')')))
    
    Categorical_Dependent2 = as.factor(Categorical_Dependent2)
    levels(Categorical_Dependent2) = levels_categorical_dependent2
    
    cat('Overall proportion of each level\n~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\n')
    Categorical_Dependent2 %>% levels() %>%
      paste0(., ': ', table(Categorical_Dependent2) / sum(table(Categorical_Dependent2)) * 100, '%', collapse = '\n') %>%
      paste0(., '\n') %>% cat
    cat('\nTo see proportions in each cell,\nplease refer to summary table.')
    
  }
})

```


### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Categorical 3</span>

```{r}

textInput('name_Categorical_Dependent3', '', placeholder = 'Variable name')
textInput('levels_categorical_dependent3', '', placeholder = 'Levels')
textInput('probability_categorical_dependent3',
          HTML('<span data-toggle="tooltip1" data-placement="right" title="Proportion of each level, overall or per cell (comma-separated), with values between 0 and 1. Values toward 0 increase proportion of first-entered levels; values toward 1 increase last-entered levels. Please check result, and if necessary, rearrange levels or increase sample size." style="border-bottom: 0.9px dotted grey;"><b> Probability </b><i class="fas fa-info-circle"></i></span>'),
          placeholder = 'Probability/ies')

reactive({
  
  if(isTruthy(input$probability_categorical_dependent3)) {
    
    Categorical_Dependent3 = rbinom(input$Total_N,
                                 # Below, count number of levels
                                 ngram::wordcount(input$levels_categorical_dependent3) - 1,  # One has to be subtracted for rbinom() to be be accurate
                                 eval(parse(text = paste0('c(', input$probability_categorical_dependent3, ')'))))
    
    # Place quotes around each factor level
    levels_categorical_dependent3 = sapply(strsplit(input$levels_categorical_dependent3, '[, ]+'), function(x) toString(dQuote(x)))
    
    # Wrap levels in c()
    levels_categorical_dependent3 = eval(parse(text = paste0('c(', levels_categorical_dependent3, ')')))
    
    Categorical_Dependent3 = as.factor(Categorical_Dependent3)
    levels(Categorical_Dependent3) = levels_categorical_dependent3
    
    cat('Overall proportion of each level\n~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\n')
    Categorical_Dependent3 %>% levels() %>%
      paste0(., ': ', table(Categorical_Dependent3) / sum(table(Categorical_Dependent3)) * 100, '%', collapse = '\n') %>%
      paste0(., '\n') %>% cat
    cat('\nTo see proportions in each cell,\nplease refer to summary table.')
    
  }
})

```


### <span style='font-weight:bold; font-size:15px; color:#0E6D00;'>Categorical 4</span>

```{r}

textInput('name_Categorical_Dependent4', '', placeholder = 'Variable name')
textInput('levels_categorical_dependent4', '', placeholder = 'Levels')
textInput('probability_categorical_dependent4',
          HTML('<span data-toggle="tooltip1" data-placement="right" title="Proportion of each level, overall or per cell (comma-separated), with values between 0 and 1. Values toward 0 increase proportion of first-entered levels; values toward 1 increase last-entered levels. Please check result, and if necessary, rearrange levels or increase sample size." style="border-bottom: 0.9px dotted grey;"><b> Probability </b><i class="fas fa-info-circle"></i></span>'),
          placeholder = 'Probability/ies')

reactive({
  
  if(isTruthy(input$probability_categorical_dependent4)) {
    
    Categorical_Dependent4 = rbinom(input$Total_N,
                                 # Below, count number of levels
                                 ngram::wordcount(input$levels_categorical_dependent4) - 1,  # One has to be subtracted for rbinom() to be be accurate
                                 eval(parse(text = paste0('c(', input$probability_categorical_dependent4, ')'))))
    
    # Place quotes around each factor level
    levels_categorical_dependent4 = sapply(strsplit(input$levels_categorical_dependent4, '[, ]+'), function(x) toString(dQuote(x)))
    
    # Wrap levels in c()
    levels_categorical_dependent4 = eval(parse(text = paste0('c(', levels_categorical_dependent4, ')')))
    
    Categorical_Dependent4 = as.factor(Categorical_Dependent4)
    levels(Categorical_Dependent4) = levels_categorical_dependent4
    
    cat('Overall proportion of each level\n~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\n')
    Categorical_Dependent4 %>% levels() %>%
      paste0(., ': ', table(Categorical_Dependent4) / sum(table(Categorical_Dependent4)) * 100, '%', collapse = '\n') %>%
      paste0(., '\n') %>% cat
    cat('\nTo see proportions in each cell,\nplease refer to summary table.')
    
  }
})

```


```{r}

# Create final data set

# Participants

Participants = reactive(data.frame(stringsAsFactors = FALSE,
                                   Participants = factor(c(rep(seq(1, input$Total_N), each = 1)))))

# Between-group

BetweenGroup1 = reactive({
  if(isTruthy(input$name_BetweenGroup1)) {
    data.frame(stringsAsFactors = FALSE,
               BetweenGroup1 = rep(c(input$BetweenGroup1_Group1, input$BetweenGroup1_Group2,
                                     input$BetweenGroup1_Group3, input$BetweenGroup1_Group4,
                                     input$BetweenGroup1_Group5, input$BetweenGroup1_Group6,
                                     input$BetweenGroup1_Group7, input$BetweenGroup1_Group8,
                                     input$BetweenGroup1_Group9, input$BetweenGroup1_Group10),
                                   each = 1,
                                   input$Total_N /
                                     sum(c(which(isTruthy(input$BetweenGroup1_Group1)),
                                           which(isTruthy(input$BetweenGroup1_Group2)),
                                           which(isTruthy(input$BetweenGroup1_Group3)),
                                           which(isTruthy(input$BetweenGroup1_Group4)),
                                           which(isTruthy(input$BetweenGroup1_Group5)),
                                           which(isTruthy(input$BetweenGroup1_Group6)),
                                           which(isTruthy(input$BetweenGroup1_Group7)),
                                           which(isTruthy(input$BetweenGroup1_Group8)),
                                           which(isTruthy(input$BetweenGroup1_Group9)),
                                           which(isTruthy(input$BetweenGroup1_Group10)))))
    ) %>% mutate_all(~ifelse(. %in% c(''), NA, .)) %>% na.omit()
  } else { data.frame(stringsAsFactors = FALSE, BetweenGroup1 = rep('1', each = 1, input$Total_N)) }
})

BetweenGroup2 = reactive({
  if(isTruthy(input$name_BetweenGroup2)) {
    data.frame(stringsAsFactors = FALSE,
               BetweenGroup2 = rep(c(input$BetweenGroup2_Group1, input$BetweenGroup2_Group2,
                                     input$BetweenGroup2_Group3, input$BetweenGroup2_Group4,
                                     input$BetweenGroup2_Group5, input$BetweenGroup2_Group6,
                                     input$BetweenGroup2_Group7, input$BetweenGroup2_Group8,
                                     input$WithinSubject2_Condition9, input$WithinSubject2_Condition10),
                                   each = 1,
                                   input$Total_N /
                                     sum(c(which(isTruthy(input$BetweenGroup2_Group1)),
                                           which(isTruthy(input$BetweenGroup2_Group2)),
                                           which(isTruthy(input$BetweenGroup2_Group3)),
                                           which(isTruthy(input$BetweenGroup2_Group4)),
                                           which(isTruthy(input$BetweenGroup2_Group5)),
                                           which(isTruthy(input$BetweenGroup2_Group6)),
                                           which(isTruthy(input$BetweenGroup2_Group7)),
                                           which(isTruthy(input$BetweenGroup2_Group8)),
                                           which(isTruthy(input$BetweenGroup2_Group9)),
                                           which(isTruthy(input$BetweenGroup2_Group10)))))
    ) %>% mutate_all(~ifelse(. %in% c(''), NA, .)) %>% na.omit()
  } else { data.frame(stringsAsFactors = FALSE, BetweenGroup2 = rep('1', each = 1, input$Total_N)) }
})

BetweenGroup3 = reactive({
  if(isTruthy(input$name_BetweenGroup3)) {
    data.frame(stringsAsFactors = FALSE,
               BetweenGroup3 = rep(c(input$BetweenGroup3_Group1, input$BetweenGroup3_Group2,
                                     input$BetweenGroup3_Group3, input$BetweenGroup3_Group4,
                                     input$BetweenGroup3_Group5, input$BetweenGroup3_Group6,
                                     input$BetweenGroup3_Group7, input$BetweenGroup3_Group8,
                                     input$WithinSubject3_Condition9, input$WithinSubject3_Condition10),
                                   each = 1,
                                   input$Total_N /
                                     sum(c(which(isTruthy(input$BetweenGroup3_Group1)),
                                           which(isTruthy(input$BetweenGroup3_Group2)),
                                           which(isTruthy(input$BetweenGroup3_Group3)),
                                           which(isTruthy(input$BetweenGroup3_Group4)),
                                           which(isTruthy(input$BetweenGroup3_Group5)),
                                           which(isTruthy(input$BetweenGroup3_Group6)),
                                           which(isTruthy(input$BetweenGroup3_Group7)),
                                           which(isTruthy(input$BetweenGroup3_Group8)),
                                           which(isTruthy(input$BetweenGroup3_Group9)),
                                           which(isTruthy(input$BetweenGroup3_Group10)))))
    ) %>% mutate_all(~ifelse(. %in% c(''), NA, .)) %>% na.omit()
  } else { data.frame(stringsAsFactors = FALSE, BetweenGroup3 = rep('1', each = 1, input$Total_N)) }
})

# Within-subject

WithinSubject1 = reactive({
  if(isTruthy(input$name_WithinSubject1)) {
    df = data.frame(stringsAsFactors = FALSE,
                    WithinSubject1 = rep(c(input$WithinSubject1_Condition1, input$WithinSubject1_Condition2,
                                           input$WithinSubject1_Condition3, input$WithinSubject1_Condition4,
                                           input$WithinSubject1_Condition5, input$WithinSubject1_Condition6,
                                           input$WithinSubject1_Condition7, input$WithinSubject1_Condition8,
                                           input$WithinSubject1_Condition9, input$WithinSubject1_Condition10),
                                         each = 1, input$Total_N)) %>%
      mutate_all(~ifelse(. %in% c(''), NA, .)) %>% na.omit()
  } else { data.frame(stringsAsFactors = FALSE, WithinSubject1 = rep('1', each = 1, input$Total_N)) }
})

WithinSubject2 = reactive({
  if(isTruthy(input$name_WithinSubject2)) {
    data.frame(stringsAsFactors = FALSE,
               WithinSubject2 = rep(c(input$WithinSubject2_Condition1, input$WithinSubject2_Condition2,
                                      input$WithinSubject2_Condition3, input$WithinSubject2_Condition4,
                                      input$WithinSubject2_Condition5, input$WithinSubject2_Condition6,
                                      input$WithinSubject2_Condition7, input$WithinSubject2_Condition8,
                                      input$WithinSubject2_Condition9, input$WithinSubject2_Condition10),
                                    each = 1, input$Total_N)) %>%
      mutate_all(~ifelse(. %in% c(''), NA, .)) %>% na.omit()
  } else { data.frame(stringsAsFactors = FALSE, WithinSubject2 = rep('1', each = 1, input$Total_N)) }
})

WithinSubject3 = reactive({
  if(isTruthy(input$name_WithinSubject3)) {
    data.frame(stringsAsFactors = FALSE,
               WithinSubject3 = rep(c(input$WithinSubject3_Condition1, input$WithinSubject3_Condition2,
                                      input$WithinSubject3_Condition3, input$WithinSubject3_Condition4,
                                      input$WithinSubject3_Condition5, input$WithinSubject3_Condition6,
                                      input$WithinSubject3_Condition7, input$WithinSubject3_Condition8,
                                      input$WithinSubject3_Condition9, input$WithinSubject3_Condition10),
                                    each = 1, input$Total_N)
    ) %>% mutate_all(~ifelse(. %in% c(''), NA, .)) %>% na.omit()
  } else { data.frame(stringsAsFactors = FALSE, WithinSubject3 = rep('1', each = 1, input$Total_N)) }
})

# Continuous dependent variables

Continuous_Dependent1 = reactive({
  if(isTruthy(input$name_Continuous_Dependent1)) {
    set.seed(input$seed)
    rnorm(input$Total_N,
          mean = eval(parse(text = paste0('c(', input$mean1, ')'))),
          sd = eval(parse(text = paste0('c(', input$sd1, ')')))) %>%
      round(digits = 3)
  } else { set.seed(input$seed)
    rnorm(input$Total_N, mean = 1, sd = 1) %>%
      round(digits = 3) }
})

Continuous_Dependent2 = reactive({
  if(isTruthy(input$name_Continuous_Dependent2)) {
    set.seed(input$seed)
    rnorm(input$Total_N,
          mean = eval(parse(text = paste0('c(', input$mean2, ')'))),
          sd = eval(parse(text = paste0('c(', input$sd2, ')')))) %>%
      round(digits = 3)
  } else { set.seed(input$seed)
    rnorm(input$Total_N, mean = 1, sd = 1) %>%
      round(digits = 3) }
})

Continuous_Dependent3 = reactive({
  if(isTruthy(input$name_Continuous_Dependent3)) {
    set.seed(input$seed)
    rnorm(input$Total_N,
          mean = eval(parse(text = paste0('c(', input$mean3, ')'))),
          sd = eval(parse(text = paste0('c(', input$sd3, ')')))) %>%
      round(digits = 3)
  } else { set.seed(input$seed)
    rnorm(input$Total_N, mean = 1, sd = 1) %>%
      round(digits = 3) }
})

Continuous_Dependent4 = reactive({
  if(isTruthy(input$name_Continuous_Dependent4)) {
    set.seed(input$seed)
    rnorm(input$Total_N,
          mean = eval(parse(text = paste0('c(', input$mean4, ')'))),
          sd = eval(parse(text = paste0('c(', input$sd4, ')')))) %>%
      round(digits = 3)
  } else { set.seed(input$seed)
    rnorm(input$Total_N, mean = 1, sd = 1) %>%
      round(digits = 3) }
})


# Categorical dependent variables

Categorical_Dependent1 = reactive({
  if(isTruthy(input$name_Categorical_Dependent1)) {
    set.seed(input$seed)
    categorical1 = rbinom(input$Total_N,
                       # Below, count number of levels
                       ngram::wordcount(input$levels_categorical_dependent1) - 1,  # One has to be subtracted for rbinom() to be be accurate
                       eval(parse(text = paste0('c(', input$probability_categorical_dependent1, ')'))))
    # Place quotes around each factor level
    levels_categorical_dependent1 = sapply(strsplit(input$levels_categorical_dependent1, '[, ]+'), function(x) toString(dQuote(x)))
    levels_categorical_dependent1 = eval(parse(text = paste0('c(', levels_categorical_dependent1, ')')))
    categorical1 = as.factor(categorical1)
    levels(categorical1) = levels_categorical_dependent1
    categorical1
  } else { set.seed(input$seed)
    rbinom(input$Total_N, 1, 1)
  }
})

Categorical_Dependent2 = reactive({
  if(isTruthy(input$name_Categorical_Dependent2)) {
    set.seed(input$seed)
    categorical2 = rbinom(input$Total_N,
                       # Below, count number of levels
                       ngram::wordcount(input$levels_categorical_dependent2) - 1,  # One has to be subtracted for rbinom() to be be accurate
                       eval(parse(text = paste0('c(', input$probability_categorical_dependent2, ')'))))
    # Place quotes around each factor level
    levels_categorical_dependent2 = sapply(strsplit(input$levels_categorical_dependent2, '[, ]+'), function(x) toString(dQuote(x)))
    levels_categorical_dependent2 = eval(parse(text = paste0('c(', levels_categorical_dependent2, ')')))
    categorical2 = as.factor(categorical2)
    levels(categorical2) = levels_categorical_dependent2
    categorical2
  } else { set.seed(input$seed)
    rbinom(input$Total_N, 1, 1)
  }
})

Categorical_Dependent3 = reactive({
  if(isTruthy(input$name_Categorical_Dependent3)) {
    set.seed(input$seed)
    categorical3 = rbinom(input$Total_N,
                       # Below, count number of levels
                       ngram::wordcount(input$levels_categorical_dependent3) - 1,  # One has to be subtracted for rbinom() to be be accurate
                       eval(parse(text = paste0('c(', input$probability_categorical_dependent3, ')'))))
    # Place quotes around each factor level
    levels_categorical_dependent3 = sapply(strsplit(input$levels_categorical_dependent3, '[, ]+'), function(x) toString(dQuote(x)))
    levels_categorical_dependent3 = eval(parse(text = paste0('c(', levels_categorical_dependent3, ')')))
    categorical3 = as.factor(categorical3)
    levels(categorical3) = levels_categorical_dependent3
    categorical3
  } else { set.seed(input$seed)
    rbinom(input$Total_N, 1, 1)
  }
})

Categorical_Dependent4 = reactive({
  if(isTruthy(input$name_Categorical_Dependent4)) {
    set.seed(input$seed)
    categorical4 = rbinom(input$Total_N,
                       # Below, count number of levels
                       ngram::wordcount(input$levels_categorical_dependent4) - 1,  # One has to be subtracted for rbinom() to be be accurate
                       eval(parse(text = paste0('c(', input$probability_categorical_dependent4, ')'))))
    # Place quotes around each factor level
    levels_categorical_dependent4 = sapply(strsplit(input$levels_categorical_dependent4, '[, ]+'), function(x) toString(dQuote(x)))
    levels_categorical_dependent4 = eval(parse(text = paste0('c(', levels_categorical_dependent4, ')')))
    categorical4 = as.factor(categorical4)
    levels(categorical4) = levels_categorical_dependent4
    categorical4
  } else { set.seed(input$seed)
    rbinom(input$Total_N, 1, 1)
  }
})

# Final data set

dataset = reactive({
  
  # General, initial structure
  
  df = data.frame(
    Participant = Participants(), BetweenGroup1(), BetweenGroup2(), BetweenGroup3(),
    WithinSubject1(), WithinSubject2(), WithinSubject3(), Categorical_Dependent1(),
    Categorical_Dependent2(), Categorical_Dependent3(), Categorical_Dependent4()
  ) %>%
    expand(
      nesting(Participants(), BetweenGroup1(), BetweenGroup2(), BetweenGroup3(), 
              Categorical_Dependent1(), Categorical_Dependent2(), Categorical_Dependent3(), 
              Categorical_Dependent4()),
      WithinSubject1(), WithinSubject2(), WithinSubject3()
    ) %>%
    cbind(Continuous_Dependent1 = Continuous_Dependent1(), 
          Continuous_Dependent2 = Continuous_Dependent2(), 
          Continuous_Dependent3 = Continuous_Dependent3(),
          Continuous_Dependent4 = Continuous_Dependent4())
  
  # Having created a general structure, remove variables that haven't been filled in by user
  # and name each variable with the user's choice
  
  # Within-subject variables
  
  # if(isTruthy(input$name_WithinSubject3)) {
  #   names(df)[names(df)=='WithinSubject1'] = input$name_WithinSubject1
  #   names(df)[names(df)=='WithinSubject2'] = input$name_WithinSubject2
  #   names(df)[names(df)=='WithinSubject3'] = input$name_WithinSubject3
  # }
  
  if(isTruthy(input$name_WithinSubject2) & !isTruthy(input$name_WithinSubject3)) {
    df = df %>% select(-WithinSubject3) %>% select_if(is.numeric) %>%
      aggregate(by = list(Participant = df$Participant, BetweenGroup1 = df$BetweenGroup1,
                          BetweenGroup2 = df$BetweenGroup2, BetweenGroup3 = df$BetweenGroup3,
                          WithinSubject1 = df$WithinSubject1, WithinSubject2 = df$WithinSubject2,
                          Categorical_Dependent1 = df$Categorical_Dependent1,
                          Categorical_Dependent2 = df$Categorical_Dependent2,
                          Categorical_Dependent3 = df$Categorical_Dependent3,
                          Categorical_Dependent4 = df$Categorical_Dependent4),
                FUN = mean)
    # names(df)[names(df)=='WithinSubject1'] = input$name_WithinSubject1
    # names(df)[names(df)=='WithinSubject2'] = input$name_WithinSubject2
  } 
  
  if(isTruthy(input$name_WithinSubject1) & !isTruthy(input$name_WithinSubject2)) {
    df = df %>% select(-c(WithinSubject2, WithinSubject3)) %>% select_if(is.numeric) %>%
      aggregate(by = list(Participant = df$Participant, BetweenGroup1 = df$BetweenGroup1,
                          BetweenGroup2 = df$BetweenGroup2, BetweenGroup3 = df$BetweenGroup3,
                          WithinSubject1 = df$WithinSubject1, 
                          Categorical_Dependent1 = df$Categorical_Dependent1,
                          Categorical_Dependent2 = df$Categorical_Dependent2,
                          Categorical_Dependent3 = df$Categorical_Dependent3,
                          Categorical_Dependent4 = df$Categorical_Dependent4),
                FUN = mean)
    # names(df)[names(df)=='WithinSubject1'] = input$name_WithinSubject1
  } 
  
  if(!isTruthy(input$name_WithinSubject1)) {
    df = df %>% select(-c(WithinSubject1, WithinSubject2, WithinSubject3)) %>% select_if(is.numeric) %>%
      aggregate(by = list(Participant = df$Participant, BetweenGroup1 = df$BetweenGroup1,
                          BetweenGroup2 = df$BetweenGroup2, BetweenGroup3 = df$BetweenGroup3,
                          Categorical_Dependent1 = df$Categorical_Dependent1,
                          Categorical_Dependent2 = df$Categorical_Dependent2,
                          Categorical_Dependent3 = df$Categorical_Dependent3,
                          Categorical_Dependent4 = df$Categorical_Dependent4),
                FUN = mean)
  }
  
  # Between-group variables
  
  # if(isTruthy(input$name_BetweenGroup3)) {
  #   names(df)[names(df)=='BetweenGroup1'] = input$name_BetweenGroup1
  #   names(df)[names(df)=='BetweenGroup2'] = input$name_BetweenGroup2
  #   names(df)[names(df)=='BetweenGroup3'] = input$name_BetweenGroup3
  # }
  
  if(!isTruthy(input$name_BetweenGroup3)) {
    df = df %>% select(-c(BetweenGroup3))
    # names(df)[names(df)=='BetweenGroup1'] = input$name_BetweenGroup1
    # names(df)[names(df)=='BetweenGroup2'] = input$name_BetweenGroup2
  } 
  
  if(!isTruthy(input$name_BetweenGroup2)) {
    df = df %>% select(-c(BetweenGroup2))
    # names(df)[names(df)=='BetweenGroup1'] = input$name_BetweenGroup1
  }
  
  if(!isTruthy(input$name_BetweenGroup1)) {
    df = df %>% select(-c(BetweenGroup1))
  }
  
  # Continuous dependent variables
  
  if(!isTruthy(input$name_Continuous_Dependent4)) {
    df = df %>% select(-c(Continuous_Dependent4))
    # names(df)[names(df)=='Continuous_Dependent1'] = input$name_Continuous_Dependent1
    # names(df)[names(df)=='Continuous_Dependent2'] = input$name_Continuous_Dependent2
    # names(df)[names(df)=='Continuous_Dependent3'] = input$name_Continuous_Dependent3
  } 
  
  if(!isTruthy(input$name_Continuous_Dependent3)) {
    df = df %>% select(-c(Continuous_Dependent3))
    # names(df)[names(df)=='Continuous_Dependent1'] = input$name_Continuous_Dependent1
    # names(df)[names(df)=='Continuous_Dependent2'] = input$name_Continuous_Dependent2
  } 
  
  if(!isTruthy(input$name_Continuous_Dependent2)) {
    df = df %>% select(-c(Continuous_Dependent2))
    # names(df)[names(df)=='Continuous_Dependent1'] = input$name_Continuous_Dependent1
  }
  
  if(!isTruthy(input$name_Continuous_Dependent1)) {
    df = df %>% select(-c(Continuous_Dependent1))
  }
  
  # Categorical dependent variables
  
  if(!isTruthy(input$name_Categorical_Dependent4)) {
    df = df %>% select(-c(Categorical_Dependent4, 'Categorical_Dependent4()'))
  }
  
  if(!isTruthy(input$name_Categorical_Dependent3)) {
    df = df %>% select(-c(Categorical_Dependent3, 'Categorical_Dependent3()'))
  }
  
  if(!isTruthy(input$name_Categorical_Dependent2)) {
    df = df %>% select(-c(Categorical_Dependent2, 'Categorical_Dependent2()'))
  }
  
  if(!isTruthy(input$name_Categorical_Dependent1)) {
    df = df %>% select(-c(Categorical_Dependent1, 'Categorical_Dependent1()'))
  }
  
  df
})

```



Summary
=======================================================================

Column {style="data-width:100%; position:static; height:1000px;"}
-----------------------------------------------------------------------

### **Summary of the data collapsed across participants**

```{r}

renderDT({
  datatable(dataset_summary(), extensions = c('Buttons', 'FixedHeader'), class = 'compact cell-border',
            options = list(order = list(1, 'asc'), dom = 'Bifrt', scroller = TRUE, fixedHeader = TRUE,
                           buttons = list(list(extend = 'csv',
                                               filename = paste0('Summary of simulation using seed number ', input$seed, ' - retrieved ',
                                                                 str_replace_all(format(Sys.time(), '%d-%b-%Y_%X-%Z'), ':', '-') %>% 
                                                                   str_replace_all('\\ ', '-'), ' - ',
                                                                 'info on GitHub repository pablobernabeu data-simulation-app')),
                                          list(extend = 'excel',
                                               filename = paste0('Summary of simulation using seed number ', input$seed, ' - retrieved ',
                                                                 str_replace_all(format(Sys.time(), '%d-%b-%Y_%X-%Z'), ':', '-') %>% 
                                                                   str_replace_all('\\ ', '-'), ' - ',
                                                                 'info on GitHub repository pablobernabeu data-simulation-app'))),
                           pageLength = nrow(dataset_summary())),
            selection = 'none')
})

```



Dataset
=======================================================================

Column {style="data-width:100%; position:static; height:1000px;"}
-----------------------------------------------------------------------

### **Final data set** 

If you wish to ensure the reproducibility of the simulated data, please download this data set as well as the parameter list (below) and keep the seed number (`r reactive(input$seed)`, also shown in the names of the downloaded files).

`r uiOutput('parameters_download_link')`

<br>

```{r}

# Rename columns

final_dataset = reactive({
  
  final = dataset()
  
  if(isTruthy(input$name_BetweenGroup1)) {
    names(final)[names(final)=="BetweenGroup1"] = input$name_BetweenGroup1
  }
  
  if(isTruthy(input$name_BetweenGroup2)) {
    names(final)[names(final)=="BetweenGroup2"] = input$name_BetweenGroup2
  }
  
  if(isTruthy(input$name_BetweenGroup3)) {
    names(final)[names(final)=="BetweenGroup3"] = input$name_BetweenGroup3
  }
  
  if(isTruthy(input$name_WithinSubject1)) {
    names(final)[names(final)=="WithinSubject1"] = input$name_WithinSubject1
  }
  
  if(isTruthy(input$name_WithinSubject2)) {
    names(final)[names(final)=="WithinSubject2"] = input$name_WithinSubject2
  }
  
  if(isTruthy(input$name_WithinSubject3)) {
    names(final)[names(final)=="WithinSubject3"] = input$name_WithinSubject3
  }
  
  if(isTruthy(input$name_Continuous_Dependent1)) {
    names(final)[names(final)=="Continuous_Dependent1"] = input$name_Continuous_Dependent1
  }
  
  if(isTruthy(input$name_Continuous_Dependent2)) {
    names(final)[names(final)=="Continuous_Dependent2"] = input$name_Continuous_Dependent2
  }
  
  if(isTruthy(input$name_Continuous_Dependent3)) {
    names(final)[names(final)=="Continuous_Dependent3"] = input$name_Continuous_Dependent3
  }
  
  if(isTruthy(input$name_Continuous_Dependent4)) {
    names(final)[names(final)=="Continuous_Dependent4"] = input$name_Continuous_Dependent4
  }
  
  if(isTruthy(input$name_Categorical_Dependent1)) {
    names(final)[names(final)=="Categorical_Dependent1"] = input$name_Categorical_Dependent1
  }
  
  if(isTruthy(input$name_Categorical_Dependent2)) {
    names(final)[names(final)=="Categorical_Dependent2"] = input$name_Categorical_Dependent2
  }
  
  if(isTruthy(input$name_Categorical_Dependent3)) {
    names(final)[names(final)=="Categorical_Dependent3"] = input$name_Categorical_Dependent3
  }
  
  if(isTruthy(input$name_Categorical_Dependent4)) {
    names(final)[names(final)=="Categorical_Dependent4"] = input$name_Categorical_Dependent4
  }
  
  final
  
})


renderDT(datatable(final_dataset(), extensions = c('Buttons', 'FixedHeader'), class="compact cell-border",
                   options = list(order = list(0, 'asc'), dom = 'Bifrt', pageLength = nrow(final_dataset()),
                                  buttons = list(list(extend = 'csv',
                                                      filename = paste0('Data simulation using seed number ', input$seed, ' - retrieved ',
                                                                        str_replace_all(format(Sys.time(), '%d-%b-%Y_%X-%Z'), ':', '-') %>%
                                                                          str_replace_all('\\ ', '-'), ' - ',
                                                                        'info on GitHub repository pablobernabeu data-simulation-app')),
                                                 list(extend = 'excel',
                                                      filename = paste0('Data simulation using seed number ', input$seed, ' - retrieved ',
                                                                        str_replace_all(format(Sys.time(), '%d-%b-%Y_%X-%Z'), ':', '-') %>%
                                                                          str_replace_all('\\ ', '-'), ' - ',
                                                                        'info on GitHub repository pablobernabeu data-simulation-app'))),
                                  scroller = TRUE, fixedHeader = TRUE),
                   selection = 'none', rownames = FALSE))

```

